Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-06-12 Thesis/chapter/03-theoretical-background.tex
AI free write 1st edit

\todo{freewrinting}: The history of AI goes back to the middle of the 20th century. At the dartmouth conference researchers from the emerging field came to gether and the begriff of ai was coined. Important people are Alan Turing, who thought alot about how to define and how to test and how to implement ai. One example is to measure against the human in playing chess. which was managed to, the human was besiegt by a computer in the early 2000. But fear not. That doesn't mean that computers are more intelligent than humans and certainly not that research is over. AI is still a young field, strongly growing and gaining ubiquitous status. Slowly creeping into every human things just like electricity hundred years ago. Now we cant - it's hard to - imagine to live without electricity. Another test ingeniused by alan turing, is that a human must communicate with a unknown entity (in written form) and guess or better ableiten if they are dealing with a machine or a human being. It is easy for humans to come up with question to bring AI out of concept, but when reading AI written articles (see GPT), it's easy to see this test being passed in the near future. 
Realms in which AI is gaining traction are: 
An interesting effect is the so called AI effect: certain fields get incorporated into AI research and practical and after some time of general use are no more considered AI such as spam filter, web searches and and. 

>>>>

\todo{freewrinting}: The history of AI goes back to the middle of the \nth{20} century. 
Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined. 
Pioneers like Alan Turing thought a lot about how to define and how to test and how to implement \gls{ai}. 
One example how to measure \gls{ai} is to let it play chess against a human, which was managed to, the human was defeated by a computer in the early 2000. 
But fear not, that doesn't mean that computers are more intelligent than humans and certainly not that research is over. 
AI is still a young field, strongly growing and gaining ubiquitous status. 
Slowly creeping into every human aspect just like electricity around one hundred years ago. 
Now we cant - it's hard to - imagine to live without electricity. 
Another test ingenioused by Alan Turing, is that a human must communicate with a unknown entity (in written form) and judge if they are dealing with a machine or a human being. 
It is easy for humans to come up with question to bring AI out of concept, but when reading AI written articles (see GPT), it's easy to see this test being passed in the near future. 
Realms in which AI is gaining traction are: 
An interesting effect is the so called \gls{ai} effect:

effect \cite{McCorduck1982,ai100} (e.g. spam filter or web search) \\

certain fields get incorporated into AI research and practical and after some time of general use are no more considered AI such as spam filter, web searches and and. 
